Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct reduction practices and raw material differences

### 2022-08-06 supp/01-size.class.Rmd
<edit index>

# read data and define number of sLMs ----
shapes <- readShapes("shapes")
shapesGM <- readland.shapes(shapes, nCurvePts = c(15, 10, 15))

@@

>>>>

# read data and define number of sLMs ----
shapes <- readShapes("shapes")
shapesGM <- readland.shapes(shapes, nCurvePts = c(15, 20, 35))

@@

Centroid size---the square root of the sum of squared distances of all landmarks from the centroid---is the measure of size used in landmark geometric morphometrics [@RN11462]. The mean centroid size was identified for elliptical bifaces from each site. All bifaces with centroid sizes larger than the mean were assigned to the `large class`; those with centroid sizes below the mean were assigned to the `small class`.

### 2022-08-06 supp/index.Rmd
<edit index>

An analysis of morphological disparity was used [@RN11107;@RN7041;@RN5694] to identify potential differences in morphological diversity between size classes.

>>>>

An analysis of morphological disparity was used to identify potential differences in morphological diversity between size classes [@RN11107;@RN7041;@RN5694].
